The Role of Variability in Learning Generalization: A Computational Modeling Approach

### 2024-05-26 Presentation/slides.qmd
slide updates

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
subtitle: "Dissertation Defense"
format: 
  html: default
    #toc: true
    #shift-heading-level-by: 1
    #toc-expand: true
  clean-revealjs:
    #theme: moon #white
    #output-ext: revealjs.html
    output-file: slides_revealjs
    slideNumber: true
    hash-type: number # Use slide numbers in the URL hash
    center: true
    scrollable: true
    chalkboard:
      theme: whiteboard
  pptx:
    incremental: true
  hugo-md:
    include: false
    html-math-method: mathjax
    output-file: slides_hugo.md
  gfm:
    output: false
    output-file: slides_gfm.md
author:
  - name: Thomas Gorman
    url: https://tegorman13.github.io
    orcid: 0000-0001-5366-5442
    affiliations:
      - name: Indiana University
        department: Psychological & Brain Sciences, Cognitive Science
params:
  start_slide: 0
#engine: knitr
---

::::: {.content-visible when-format="html" unless-format="revealjs"}
\
[Click here](../paper.qmd) to open the dissertation manuscript.\
\
\
\

\

@@

## Introduction

@@

## Project 1 - Hit The Target (HTT)

@@

## Project 1 - Task & Procedure

:::: {.columns}
::: {.column width="60%"}
<!-- ![](assets/methodsFig1.png) -->

@@

::: {.column width="40%"}
- **Training Stage** - 200 training trials. Constant groups throws from single position. Varied group 60 trials from 2 locations. 
- **Transfer Stage** - All subjects tested from both positions they were trained, and the positions trained by other group
- **Data recorded** - For every throw, recorded the X velocity and Y velocity of ball at release
:::

@@

@@

## Project 2 - Variability and Extrapolation in a Function Learning Task

@@

## Task

@@

## Project 2 - ALM

@@

## General Discussion

>>>>

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
subtitle: "Dissertation Defense"
page-layout: full
aliases:
  - /slides.html
format: 
  html: default
    #toc: true
    #shift-heading-level-by: 1
    #toc-expand: true
  clean-revealjs:
    #theme: moon #white
    #output-ext: revealjs.html
    output-file: slides_revealjs
    slideNumber: true
    hash-type: number # Use slide numbers in the URL hash
    center: true
    scrollable: true
    chalkboard:
      theme: whiteboard
  # pptx:
  #   incremental: false
  # hugo-md:
  #   include: false
  #   html-math-method: mathjax
  #   output-file: slides_hugo.md
  # gfm:
  #   output: false
  #   output-file: slides_gfm.md
author:
  - name: Thomas Gorman
    url: https://tegorman13.github.io
    orcid: 0000-0001-5366-5442
    affiliations:
      - name: Indiana University
        department: Psychological & Brain Sciences, Cognitive Science
params:
  start_slide: 0
#engine: knitr
---

::::: {.content-visible when-format="html" unless-format="revealjs"}
\
[Click here](../paper.qmd) to open the dissertation manuscript.\
\
\
\
\

@@

# Introduction

@@

# Project 1

@@

## Hit The Target Task

:::::: column-page-right
::::: {.columns}
:::: {.column width="60%"}

@@

@@

:::: {.column width="40%"}
- **Training Stage** - 200 training trials. Constant groups throws from single position. Varied group 60 trials from 2 locations. 
- **Transfer Stage** - All subjects tested from both positions they were trained, and the positions trained by other group
- **Data recorded** - For every throw, recorded the X velocity and Y velocity of ball at release
::::

:::::
::::::

@@

# Project 2 - Variability and Extrapolation in a Function Learning Task

@@

## Hit The Wall Task

@@

# Project 2 - ALM

@@

# General Discussion
